\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-20 paper.tex
balance citations in the last page
Small typos fixed.
updates to abstract

@@

\subsection*{Abstract}
Testing distributed systems is challenging due to multiple sources of nondeterminism. Conventional testing techniques are ineffective in preventing serious but subtle bugs from reaching production. Formal techniques, such as the use of TLA+ in Amazon Web Services, can only verify high-level specifications of systems at the level of logic-based models, and fall short of checking the actual executable code. In this paper, we present a new framework for testing distributed storage systems. Our approach applies systematic testing to thoroughly check that the executable code adheres to its high-level specifications, which significantly improves coverage of important system behaviors.

Our framework has been applied to three distributed storage systems in the Microsoft Azure platform. In the process, numerous bugs were identified, reproduced, confirmed and fixed. These bugs required subtle combination of concurrency and failures, making them extremely difficult to find with conventional testing techniques. An important advantage of our approach is that a bug is uncovered in a small setting and witnessed by a full system trace, which dramatically increases the productivity of debugging.

@@

>>>>

\usepackage{balance}

@@

\subsection*{Abstract}
Testing distributed systems is challenging due to multiple sources of nondeterminism. Conventional testing techniques, such as unit and stress testing, are ineffective in preventing serious but subtle bugs from reaching production. Formal techniques, such as TLA+, can only verify high-level specifications of systems at the level of logic-based models, and fall short of checking the actual executable code. In this paper, we present a new methodology for testing production distributed storage systems. Our approach applies systematic testing to thoroughly check that the executable code adheres to its high-level specifications, which significantly improves coverage of important system behaviors.

Our technique has been applied to three production distributed storage systems in the Microsoft Azure platform. In the process, numerous bugs were identified, reproduced, confirmed and fixed. These bugs required a subtle combination of concurrency and failures, making them extremely difficult to find with conventional testing techniques. An important advantage of our approach is that a bug is uncovered in a small setting and witnessed by a full system trace, which dramatically increases the productivity of debugging.

@@

% Balances the bibliography in the last page
\balance
